formula1

### 2020-06-09 inst/f1points.Rmd
complete caching and all results

```{r,label=calcpoints,echo=TRUE,cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

```{r,label=montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)
points3 <- c(1, 1,1,1,1,1,0,0,0,0,0)
```

```{r,label=montecarlo_doer1, cache=TRUE}
o1 <- replicate(1000,resampling(m,f2017,points=points1))
```

```{r,label=montecarlo_doer2, cache=TRUE}
o2 <- replicate(1000,resampling(m,f2017,points=points2))

```{r,label=montecarlo_doer3, cache=TRUE}
o3 <- replicate(1000,resampling(m,f2017,points=points3))
```

```{r,label=montecarlo_shower}
plot(table(o1))
plot(table(o2))
plot(table(o3))

table(o1)
table(o2)
table(o3)

mean(o1)
mean(o2)
mean(o3)

M <- rbind(tabulate(o1+1),tabulate(o2+1),tabulate(o3+1))
dimnames(M) <- list(system=LETTERS[1:3],correct=0:11)
M
```

```{r}
out <- data.frame(rbind(cbind("A",o1),cbind("B",o2),cbind("C",o3)))
colnames(out) <- c("system","correct")
head(out)
tail(out)
summary(lm(correct~system,data=out))
```

>>>>

```{r,label=calcpoints,echo=TRUE,cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

```{r,label=montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
```

```{r,label=montecarlosetup3}
points_real
o_real <- function(n){replicate(n,resampling(m,f2017,points=points_real))}
```

now do it:

```{r,label=montecarlorealpointsdoer,cache=TRUE}
or <- o_real(1000)
```

Now some more, top n:

```{r,label=defineotop, cache = TRUE}
o_top <- function(top,n=100){replicate(n,resampling(m,f2017,points=rep(1,top)))}
```

```{r,label=executeotop1, cache = TRUE}
ot1 <- o_top(1,n=1000)
```

```{r,label=executeotop2, cache = TRUE}
ot2 <- o_top(2,n=1000)
```

```{r,label=executeotop3, cache = TRUE}
ot3 <- o_top(3,n=1000)
```

```{r,label=executeotop4, cache = TRUE}
ot4 <- o_top(4,n=1000)
```

```{r,label=executeotop5, cache = TRUE}
ot5 <- o_top(5,n=1000)
```

now some other schemes:

```{r,label=defineotherschemes}
o_zip <- function(n=100){replicate(n,resampling(m,f2017,points=1/seq_len(top)))}
o_exp <- function(p,n=100){replicate(n,resampling(m,f2017,points=p^seq_len(top)))}
```

and

```{r,label=ozcalculator,cache=TRUE}
oz <- o_zip(1000)
```

```{r,label=oecalculator,cache=TRUE}
oe <- o_exp(0.5,1000)
```

look:

```{r}
M <- rbind(
	tabulate(or +1,nbins=12),
	tabulate(ot1+1,nbins=12),
	tabulate(ot2+1,nbins=12),
	tabulate(ot3+1,nbins=12),
	tabulate(ot4+1,nbins=12),
	tabulate(ot5+1,nbins=12),
	tabulate(oz +1,nbins=12),
	tabulate(oe +1,nbins=12)
	)
dimnames(M) <- list(system=c("real",paste("top",seq_len(5)),"oz","oe"),correct=0:11)
M
```
